Parametric controls on vegetation responses to biogeochemical forcing in the CLM5

### 2019-07-02 main_revision.tex

The impact of \emph{slatop} on fertilization was different at every site. For MET, \emph{slatop} was the most important control over N responses, with higher values allowing a greater LAI/GPP feedback in response to the N fertilization. At NWR, the opposite behaviour was found, with high SLA reducing the impact of N in cases where the pre-fertilization LAI meant that a saturating response of GPP was found. At HVF, higher values of \emph{slatop} slightly reduced both CO$_{2}$ and N fertilization for the same reason (although the range of variation at HVF is only 5\% between the highest and lowest values, as opposed to 40\% at NWR).

Despite its strong impact on the system state,\emph{froot\_leaf} had very little impact on fertilization responses, except in the case of very low values at Metolius, where it increased the CO$_{2}$ responsiveness, and at Harvard, where low values decrease both responses. At Harvard the low root allocation runs had higher initial LAI, and thus the responsiveness of the system to fertilization is lower since the feedback from LAI to GPP (which is a non-linear response related to the saturation of light interception).

@@

\emph{grperc}, or the degree to which growth is 'taxed', is constant and not responsive to any of the physiological processes upstream that depend on fertilization, thus, at most sites, its impacts are minimal, or indirect.

@@

 \begin{figure}[h]
     \includegraphics[width=1.2\textwidth]{matlab/figures/MAY19jp_STATE_-r200_NWR_y2000.png}
     \caption{Response of control model states and fluxes to parameter perturbation across -1 to +1 range of parameter variation (Table \ref{table_ranges}) at Niwot Ridge.}
     \label{NR1 state}
 \end{figure}

 \begin{figure}[h]
     \includegraphics[width=1.2\textwidth]{matlab/figures/MAY19jp_STATE_-r200_CAX_y2000.png}
     \caption{Response of control model states and fluxes to parameter perturbation across -1 to +1 range of parameter variation (Table \ref{table_ranges}) at Caxiuan\~a National Forest}
     \label{CAX state}
  \end{figure}

 \begin{figure}[h]
     \includegraphics[width=1.2\textwidth]{matlab/figures/MAY19jp_STATE_-r200_HVF_y2000.png}
     \caption{Response of control model states and fluxes to parameter perturbation across -1 to +1 range of parameter variation (Table \ref{table_ranges}) at Harvard Forest}
     \label{HVF state}
 \end{figure}

 \begin{figure}[h]
     \includegraphics[width=1.2\textwidth]{matlab/figures/MAY19jp_STATE_-r200_MET_y2000.png}
     \caption{Response of control model states and fluxes to parameter perturbation across -1 to +1 range of parameter variation (Table \ref{table_ranges}) at Metolius Forest}
     \label{MET state}
 \end{figure}

>>>>

The impact of \emph{slatop} on fertilization was different at every site (figs. \ref{GPP_CN}, figures \ref{LAI_CN}). For MET, \emph{slatop} was the most important control over N responses, with higher values allowing a greater LAI/GPP feedback in response to the N fertilization. At NWR, the opposite behaviour was found, with high SLA reducing the impact of N in cases where the pre-fertilization LAI meant that a saturating response of GPP was found. At HVF, higher values of \emph{slatop} slightly reduced both CO$_{2}$ and N fertilization for the same reason (although the range of variation at HVF is only 5\% between the highest and lowest values, as opposed to 40\% at NWR).

\emph{froot\_leaf} had contrasting impacts at different sites.  At MET,  where low values increased the CO$_{2}$ fertilization, probably due to the increased drought stress under those conditions. At HVF, low \emph{froot\_leaf} decreased both CO$_{2}$ and N fertilization on account of higher initial LAI, mirroring the respnse to \emph{slatop}.

@@

@@

 \begin{figure}[h]
     \includegraphics[width=1.2\textwidth]{matlab/figures/MAY19jp_STATE_y1999.png}
     \caption{Response of control model states and fluxes to parameter perturbation across -1 to +1 range of parameter variation (Table \ref{table_ranges}) for GPP, NPP, LAI and N$+{leaf}$ at the CAX, NWR, HVF and MET sites}
     \label{NR1 state}
 \end{figure}
